\documentclass[main.tex]{subfile}

\begin{document}

% document text goes here
\section{Introduction} 
\label{sec:introduction}

Most industrial robotic applications today involve repetative motion tasks, with
little change in the operations of the robots themselves. Typically they are
programmed to optimally perform a single task. However today, with the growing
rates of production and ranging environment types we find that robots are needed
in more dynamic environments. For example Amazon has begun seeking robots that
can perform item selection in warehouses \cite{amazon} which requires the robots
to be aware of robots surrounded in a changing environment. Consider also the
cost of programming robots to perform very specific tasks. For industrial
settings where the product may change from day to day - such as glass
manufacturing - it is difficult to constantly reprogram and calibrate a robot to
conform its kinematic path planning algorithms to suite environment or product
constraints. 

Model predictive controllers (or MPCs) boast two solutions to the changing
environment and constraints problem. First, MPC algorithms allow us to use
kinematic models of the robot into the problem directly - this is more a legacy
system support to older control methods. Second, and more importantly, we can
incorporate system (both robotic and environmental) constraints on our control
model. According to \cite{autoVehicle} MPC has been mostly restricted to slower
responding systems such as chemical manufacturing facilities. Recent approaches
to autonomous vehicle applications have integrated MPC algorithms as a means of
path planning \cite{auv,uphill} and used improved optimization stage algorithms
(we will explain this further in \secref{sbmpc}) for generating flexible and
optimal controller outputs. This optimization algorithm is known as sample-based
model controller (SBMPC).

% section introduction (end)

\end{document}
